---
title: "MXN601 Worksheet 01"
author: "Joshua Bon & Christopher Drovandi"
date: "`r Sys.Date()`"
output: tint::tintPdf
bibliography: ../src/worksheets.bib
link-citations: yes
header-includes:
    - \usepackage{fancyhdr}
    - \usepackage{floatrow}
    - \floatsetup[figure]{capposition=top}
params:
  tutor_name: "Chris"
  show_solutions: FALSE
---

```{r template-header, child='../src/template-header.Rmd', eval = TRUE}

```

```{r ws-setup, include=FALSE}
  # if problems with knitting directory:
  # set Knit Directory = Document Directory

  # install libraries needed for worksheet
  library(dplyr)
  library(ggplot2)

  # Make notes here:
  # - chunk `instructions-header` currently turned off. 
  #     Set `eval = TRUE` to use (and update file).
  #
  #

```

> A theory is just a mathematical model to describe the observations.
>
> `r tint::quote_footer('---Karl Popper')`^[[Sir Karl Popper](https://en.wikipedia.org/wiki/Karl_Popper) was one of the greatest 20th century philosophers of science. He is famous for championing [empirical falsification](https://en.wikipedia.org/wiki/Falsifiability), the basis of modern science.] 

> All models are wrong, but some are useful.
>
> `r tint::quote_footer('---George E. P. Box')`^[[Dr George Box](https://en.wikipedia.org/wiki/George_E._P._Box) was an eminent 20th century statistician. Box-Jenkins models and Box-Cox transformations are just some of his contributions.] 

```{r instructions-header, child='../src/instructions-header.Rmd', eval = FALSE, echo=FALSE}
  
```

# Recap: Multivariate distributions
Multivariate distributions concisely describe two or more random variables and their interdependent stochasticity. This is particularly useful when we have some phenomena where the outcomes are multivariate and dependent on each other. For example, the locations of sightings of feral foxes in Queensland will have a longitudinal and latitudinal value.

# Theory questions

## Question 1

```{r theory-question-1, child='../question-bank/id0001-discrete-bivariate-rv-independence.Rmd', eval = TRUE}
  
```

```{r theory-solution-1, child='../solution-bank/id0001-discrete-bivariate-rv-independence.Rmd', eval = params$show_solutions}
  
```


## Question 2

```{r theory-question-2, child='../question-bank/id0003-discrete-mix-poisson.Rmd', eval = TRUE}
  
```

## Question 3

```{r theory-question-3, child='../question-bank/id0002-compound-exp-exp.Rmd', eval = TRUE}

```

## Question 4

```{r theory-question-4, child='../question-bank/id0004-bivariate-normal-marginal-conditional.Rmd', eval = TRUE}
  
```

# Practical questions

## Question 5
```{r prac-question-5, child='../question-bank/id0005-multivariate-normal-anomaly-detection.Rmd', eval = TRUE}
  
```

