---
title: "MXN601 Worksheet 01"
author: "Joshua Bon & Christopher Drovandi"
date: "`r Sys.Date()`"
output: tint::tintPdf
bibliography: ../src/worksheets.bib
link-citations: yes
header-includes:
    - \usepackage{fancyhdr}
    - \usepackage{floatrow}
    - \floatsetup[figure]{capposition=top}
params:
  tutor_name: "Chris"
  show_solutions: FALSE
---

```{r template-header, child='../src/template-header.Rmd', eval = TRUE}

```

```{r ws-setup, include=FALSE}
  # if problems with knitting directory:
  # set Knit Directory = Document Directory

  # install libraries needed for worksheet
  library(dplyr)
  library(ggplot2)

  # Make notes here:
  # - chunk `instructions-header` currently turned off. 
  #     Set `eval = TRUE` to use (and update file).
  #
  #

```

> A theory is just a mathematical model to describe the observations.
>
> `r tint::quote_footer('---Karl Popper')`^[[Sir Karl Popper](https://en.wikipedia.org/wiki/Karl_Popper) was one of the greatest 20th century philosophers of science. He is famous for championing [empirical falsification](https://en.wikipedia.org/wiki/Falsifiability), the basis of modern science.] 

> All models are wrong, but some are useful.
>
> `r tint::quote_footer('---George E. P. Box')`^[[Dr George Box](https://en.wikipedia.org/wiki/George_E._P._Box) was an eminent 20th century statistician. Box-Jenkins models and Box-Cox transformations are just some of his contributions to statistics.] 

```{r instructions-header, child='../src/instructions-header.Rmd', eval = FALSE, echo=FALSE}
  
```

# Theory questions

## Question 1

```{r theory-question-1, child='../question-bank/id0001-discrete-bivariate-rv-independence.Rmd', eval = TRUE}
  
```

```{r theory-solution-1, child='../solution-bank/id0001-discrete-bivariate-rv-independence.Rmd', eval = params$show_solutions}
  
```


## Question 2

```{r theory-question-2, child='../question-bank/id0003-discrete-mix-poisson.Rmd', eval = TRUE}
  
```

```{r theory-solution-2, child='../solution-bank/id0003-discrete-mix-poisson.Rmd', eval = params$show_solutions}
  
```

## Question 3

```{r theory-question-3, child='../question-bank/id0002-compound-exp-exp.Rmd', eval = TRUE}

```

```{r theory-solution-3, child='../solution-bank/id0002-compound-exp-exp.Rmd', eval = params$show_solutions}
  
```

# Practical questions

We will now practise simulating some mixture random variables in `R`. 
If necessary, use your answers in the theory section of this worksheet to assist you.

## Question 4
```{r prac-question-4, child='../question-bank/id0010-simulating-mixtures.Rmd', eval = TRUE}
  
```

```{r prac-solution-4, child='../solution-bank/id0010-simulating-mixtures.Rmd', eval = params$show_solution}
  
```

## Question 5
```{r prac-question-5, child='../question-bank/id0005-multivariate-normal-anomaly-detection.Rmd', eval = TRUE}
  
```

```{r prac-solution-5, child='../solution-bank/id0005-multivariate-normal-anomaly-detection.Rmd', eval = TRUE}
  
```
